\cvsection{Hard Skills}
\begin{itemize}
  \item \textbf{Platforms}: Palantir Foundry, Oracle, GCP (Vertex AI, Big Query)
  \item \textbf{Framework/Languages}: Python (PySpark, Pandas, Tensorflow, Scikit-Learn), SQL, C, JavaScript, HTML, CSS, React, C++, Matlab, Typescript, Java.
  \item \textbf{Certifications}: \href{https://verify.skilljar.com/c/w9z3dnmtv68y}{Palantir Data Engineer}, \href{https://verify.skilljar.com/c/gx72n6ke6ybo}{Palantir Data Scientist}, \href{https://verify.skilljar.com/c/42kbrbf6i9cq}{Palantir Application Developer}, \href{https://verify.skilljar.com/c/8po7zjfgt25o}{Palantir Data Analyst}, \href{https://verify.skilljar.com/c/yy4f9p52gbfr}{Palantir Solution Architect}.

  
\end{itemize}

\cvsection{EDUCATION}

\cvevent{Master's Degree in Computer Science and Engineering}{Politecnico di Milano}{2020--2022}{Milan, p.za L. da Vinci}
\textbf{Language}: English.\\
\textbf{Thesis}: \textit{\href{https://www.politesi.polimi.it/handle/10589/204539}{Read here my thesis.}}\\
\textbf{Bachelor degree thesis}: \textit{\href{https://github.com/lentinip/ing-sw-2019-Lentini-Marazzi-Marini}{See code here.}}


\cvsection{Languages}

\cvskill{Italian}{5}{ proficiency}

\cvskill{English}{5}{ proficiency}
% \divider

\cvsection{HOBBIES}

I am a passionate and curious guy who loves cultivating hobbies. I have a strong passion for \textbf{cooking}. I enjoy making pizza, panettone, and preparing \textbf{cocktails}. Additionally, I have a small collection of gins. As a true wine lover, I have achieved the first-level \textbf{sommelier} qualification. In my free time, there's nothing I enjoy more than \textbf{traveling}. I always bring my camera with me to capture \href{https://mmarini.it/gallery}{beautiful places I visit} (in 2015 I won Liliana Urtamonti \textbf{photography} contest with \href{https://www.instagram.com/p/1Ql0DrivyoekSE2An1JIdCRMaRkLcDW62WAho0/}{this shoot}). Sports also play an important role in my life, I have participated in a variety of \textbf{sports} including skiing, soccer, paddle, beach volley and basketball.

\divider

\footnotesize{I hereby authorize the use of my personal data in accordance to the GDPR 679/16 - "European regulation on the protection of personal data".}

